Understanding School Shootings: Analyzing Trends, Demographics, and Geographic Factors Using Bayesian Methods

### 2024-12-15 paper/paper.qmd
update typo
update typo

We used the`R`programming language [@citeR], the `here` package [@here],the `dplyr` package [@R_dplyr], the `tidyr` package [@R_tidyr], the `maps` package [@R_maps], the `ggplot2` package [@R_ggplot2], and the`scale` package [@R_scales] to clean the data. We used the `tidyverse` package [@tidyverse], the `maps` package [@maps], the `ggplot2` package [@R_ggplot2], the `knitr` package [@knitr], the `kableExtra` package [@kableExtra] to plot the dataset and the visualization.

>>>>

We used the`R`programming language [@citeR], the `arrow` package [@parquet] to save and read the data, the `here` package [@here],the `dplyr` package [@R_dplyr], the `tidyr` package [@R_tidyr], the `maps` package [@R_maps], the `ggplot2` package [@R_ggplot2], and the`scale` package [@R_scales] to clean the data. We used the `tidyverse` package [@tidyverse], the `maps` package [@maps], the `ggplot2` package [@R_ggplot2], the `knitr` package [@knitr], the `kableExtra` package [@kableExtra] to plot the dataset and the visualization.
